Exploiting First-Class Arrays in Fortran for Accelerator Programming

### 2010-12-15 opencl/papers/source-to-source.tex
minor change

Performance measurements were made comparing the transformed code with
different versions of the serial shallow-water code.  The serial versions
include the original written in C and two Fortran versions: one using copy
semantics for the regions and one using reference semantics.  We also compare
with a hand written OpenCL implementation that was optimized for local memory
usage (no array temporaries).  The measurments were made using an NVIDIA Fermi
GPU (TODO - need model numbers) running at XXX Hz and a VENDOR hexacore CPU
running at XXX Hz.  The compilers were gfortran and gcc VERSIONS with
optimization of -O3.

>>>>

Performance measurements were made comparing the transformed code with
different versions of the serial shallow-water code.  The serial versions
include the original written in C and two Fortran versions: one using copy
semantics for the regions and one using reference semantics.  We also compare
with a hand written OpenCL implementation that was optimized for local memory
usage (no array temporaries).  The measurments were made using an NVIDIA Tesla C2050
GPU (TODO - need model numbers) running at XXX Hz and an Intel XXX hexacore CPU
running at XXX Hz with 2.56 GB of RAM.  The compilers were gfortran and gcc VERSIONS with
optimization of -O3.
